A Descriptive Analysis of How Psychology Journals Handle Post-Publication

### 2024-01-05 manuscript/manuscript_NHB.Rmd
Added COPE data
updated to include COPE results coded in-text

library(papaja) # article template
library(tidyverse)
library(ggplot2) # figure creation
library(ggrepel) # for ggplot text labels
library(patchwork) # for multipanel plot layouts
library(RColorBrewer) # data visualisation
library(dplyr)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(janitor) # for data munging
library(tidylog) # for inline code feedback
library(here) # for finding files
library(binom) # for calculating CIs
library(citation) # for organizing citations
library(tinytex)
```

@@

### Table *XX*

@@

@@

>>>>

library(papaja) # article template
library(tidyverse)
library(ggplot2) # figure creation
library(ggrepel) # for ggplot text labels
library(patchwork) # for multipanel plot layouts
library(RColorBrewer) # data visualisation
library(dplyr)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(janitor) # for data munging
library(tidylog) # for inline code feedback
library(here) # for finding files
library(binom) # for calculating CIs
library(citation) # for organizing citations
library(tinytex)
library(english) # for displaying code generated numbers as written 
```

@@

### Table *XX*
[*Insert table of results*]

@@

```{r COPE status in prominent sample, echo=FALSE, message=FALSE}
# COPE membership status among prominent journals accepting PPC
prominent_PPCy <- dj_prominent %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>% # keep only journals that accept PPC
  summarise(count = n()) # total number journals accepting PPC

prom_copeY_PPC <- dj_prominent %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
  summarise(count = n()) # number of COPE journals accepting PPC

prom_copeN_PPC <- dj_prominent %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
  summarise(count = n()) # number of non-COPE journals accepting PPC

# COPE membership status among prominent journals NOT accepting PPC
prominent_PPCn <- dj_prominent %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that accept PPC
  summarise(count = n()) # total number journals accepting PPC

prom_copeY_PPCn <- dj_prominent %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
  summarise(count = n()) # number of COPE journals accepting PPC

prom_copeN_PPCn <- dj_prominent %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
  summarise(count = n()) # number of non-COPE journals accepting PPC

Of the `r paste(prominent_PPCy$count)` journals that accepted post-publication critiques (including the six implicitly implied through archive examples), `r paste(prom_copeY_PPC$count, "(", round((prom_copeY_PPC$count / prominent_PPCy$count) * 100, 1), "%)", sep = "")` were COPE members and `r paste(as.english(prom_copeN_PPC$count), " (", round((prom_copeN_PPC$count / prominent_PPCy$count) * 100, 1), "%)", sep = "")` were not. Of the `r paste(prominent_PPCn$count)` journals that had no critique policy, `r paste(prom_copeY_PPCn$count, "(", round((prom_copeY_PPCn$count / prominent_PPCn$count) * 100, 1), "%)", sep = "")` were COPE members, including both of those with explicit statements that they do not accept unsolicited critiques.

@@

```{r COPE status in random sample, echo=FALSE, message=FALSE}
# COPE membership status among randomly-sampled journals accepting PPC
random_PPCy <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>% # keep only journals that accept PPC
  summarise(count = n()) # total number journals accepting PPC

rand_copeY_PPC <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
  summarise(count = n()) # number of COPE journals accepting PPC

rand_copeN_PPC <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "ARCHIVE") %>%
  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
  summarise(count = n()) # number of non-COPE journals accepting PPC

# COPE membership status among prominent journals NOT accepting PPC
random_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>% # keep only journals that accept PPC
  summarise(count = n()) # total number journals accepting PPC

rand_copeY_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "TRUE") %>% # Keep only COPE journals (that accept PPC)
  summarise(count = n()) # number of COPE journals accepting PPC

rand_copeN_PPCn <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "NO IMPLICIT" | has_ppc == "NO EXPLICIT") %>%
  filter(cope == "FALSE") %>% # Keep only non-COPE journals (that accept PPC)
  summarise(count = n()) # number of non-COPE journals accepting PPC

Of the `r paste(random_PPCy$count)` journals that accepted post-publication critiques (including the three implicitly implied through archive examples), `r paste(rand_copeY_PPC$count, "(", round((rand_copeY_PPC$count / random_PPCy$count) * 100, 1), "%)", sep = "")` were COPE members and `r paste(as.english(rand_copeN_PPC$count), " (", round((rand_copeN_PPC$count / random_PPCy$count) * 100, 1), "%)", sep = "")` were not. Of the `r paste(random_PPCn$count)` journals that had no critique policy, `r paste(rand_copeY_PPCn$count, "(", round((rand_copeY_PPCn$count / random_PPCn$count) * 100, 1), "%)", sep = "")` were COPE members, including the one with an explicit statement that they do not accept unsolicited critiques.
